Universal Anonymous Signatures

### 2022-08-02 prism-backend/research/gsac/formal-uas.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.
Updating proofs.

\begin{description}
\item[$\fissue: (\upk,\attrs,\lbrace (\cid_i,\cattrs_i)
  \rbrace_{i \in [n]}) \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour
  of \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, the former is chosen on a
per-signature basis, probably after negotiation between signer and verifier, and
governs the information revealed at signing time. On the other hand, \finsp
governs the information that may be revealed after signing, and is defined by
openers when they set up their key pair. Thus even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function. In the sequel, we restrict to
\UAS-acceptable functions, which we will also use to give \CUASGen restrictions.
Both concepts are defined next.

% \begin{definition}{(\UAS-acceptable functions)}
%   \label{def:uas-acc-func}
%   We say that a \fissue (similarly, \feval or \finsp) function chosen from some
%   family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
%   is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
%   (similarly, \feval or \finsp), it is at least computationally unfeasible to
%   recover the $(\upk,\usk)$ value used to produce it.
% \end{definition}

@@

% To summarize the previous, we depict in \figref{fig:uas-signature} the structure
% of an \UAS signature, including its main components and how they enable the
% previously stated generalization claims.

% \begin{figure}[ht!]
%   \centering
%   %\input{figures/uas-signature.tex}
%   \caption{Structure of an \UAS signature.}
%   \label{fig:uas-signature}
% \end{figure}

@@

        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\cscid_0,\attrs)) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\cscid_1,\attrs)): \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{description}
\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. Requires that the
  owner commits to, and proves knowledge of, \usk. It also requires that any
  additional credential supporting the request be a valid credential (signed by
  some issuer) and bound to \usk. Finally, it also enforces the
  corresponding \fissue policy.
\item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. Ensures that
  signatures ``encode'' the correct signature evaluation and opening values, and
  that any credential used to create the signature is bound to the same \usk.
\item[$\NIZKRel_{\Open}$:] For NIZK proofs at opening time. Ensures that the
  utility information extracted by the \Open algorithm is correct.
\end{description}

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.
  \todo{Is $\C = \CCommit(\usk;r)$ at Issue needed now that \upk is added?}}
  \label{fig:nizkrels}
\end{figure}

From them, we build \CUASGen as follows.
\todo{Check if \SSetup etc is still needed...}

\paragraph{$\parm \gets \Setup(\secpar)$.} %
The setup process essentially generates the public parameters for all the
building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
\SBCMSetup(\secpar)$, $\Sparm \gets \SSetup(\secpar)$, $\Eparm \gets
\ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}
(\secpar)$, $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $
(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},
\NIZKcrs_{\Open})$. % Many of these parameter setup algorithms can
% actually be run by separate entities. For simplicity of exposition, we bundle
% them together here.

@@

\paragraph{$(\upk,\usk) \gets \KeyGen(\parm)$.} %
Each user first parses \parm as $(\cdot,\SBCMparm,
\cdot,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\SBCMvk,\SBCMsk) \gets
\SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,\SBCMvk)$, $\usk \gets \SBCMsk$,
and returns $(\upk,\usk)$.

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
Each opener first parses \parm as $(\cdot,\cdot,
\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
(\Ssk,\finsp)$, $\opk \gets (\Sparm,\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk
\gets (\Ssk,\Edk)$.

\paragraph{$\ipk \gets \ISet((\upk,\usk),\fissue)$.} %
A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
returns \ipk.

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\cidu,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
  \attrs),\Issue(\isk,\cidi,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
attests attributes $\cattrs_i$. The user requests a signature on a commitment to
the user key, as well as on $\cid=(\cidi,\cidu)$ and the attributes in \attrs.
In addition, the user proves correct computation of the \fissue function set by
the issuer based on the $\cred_i$ credentials and its user key pair.
This is essentially achieved through an execution of an \SBCM interactive
signing protocol with $\NIZKRel_{\Issue}$ as NP relation. Since \fissue is
evaluated by the user, but depends on the \cidi value chosen by the issuer, the
issuer first needs to send \cidi to the user.
Then both issuer and user interact to produce the \SBCM signature, where the
user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
\cattrs_i,\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the
issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
\rbrace_{i\in[n]})$. The credential \cred produced by the user is the result of
the interactive signing protocol, whereas the issuer produces $(\yissue,
\utrans)$, where \yissue is the output of \fissue, and \utrans is the
communication transcript, which is a $(\Ccom,(\cid,\attrs),\lbrace
\ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple.

\paragraph{$\Sig \gets \Sign(\usk,\opk,
  \sCred=(\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)\rbrace_{i\in[n]}),
  \msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
The user first evaluates $\Yeval = (\yeval^0,\yeval^1) \gets \feval (\usk,
\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$.
Then, parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
(this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
\yeval^1),\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
\yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r')$ for some fresh
randomness $r'$. Finally, the user
computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
\lbrace(\cid_i,\cattrs_i,\cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r),(\msg,
\feval,\yeval^0,\cinsp,\lbrace \ipk_i\rbrace_{i\in[n]},\Eek))$ and outputs
$(\sig = (\NIZKproof,\cinsp),\yeval^0)$. Note that, depending on the value of
\Yeval and \yinsp, the user may decide to abort
the signing if the resulting values are too privacy-threatening.

@@

\begin{theorem}[Issuance anonymity of \CUASGen]
  \label{thm:issue-anonymity-uas}
  If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
  zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
  defined in \defref{def:issue-anonymity-uas}.
\end{theorem}

>>>>

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
  signature,  both can in addition be used to modulate the behaviour of
  \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, the former is chosen on a
per-signature basis, probably after negotiation between signer and verifier, and
governs the information revealed at signing time. On the other hand, \finsp
governs the information that may be revealed after signing, and is defined by
openers when they set up their key pair. Thus even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function. In the sequel, we restrict to
\UAS-acceptable functions, defined as follows:

\begin{definition}{(\UAS-acceptable functions)}
  \label{def:uas-acc-func}
  We say that a \fissue function chosen from some family \famfissue is
  \UAS-acceptable if its outputs are hiding with respect to its \upk and
  $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
  %
  Similarly, a \feval function chosen from some family \famfeval is
  \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
  respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
\end{definition}

That is, at a high level we require that \fissue and \feval functions do not
reveal anything about the signer. \todo{Since the concept is quite intuitive, we
  defer the formal definition to \appref{app:XXX}}. We give in
\secref{ssec:generic-construction-uas}
a generic \CUASGen construction that assumes \UAS-acceptable functions. Next, we
define the concept of \CUASGen restrictions. Briefly, these are special cases of
our generic construction that target a concrete variant of the utility-privacy
tradeoff by defining concrete \fissue, \feval and \finsp functions. Security of
\CUASGen implies security of its restrictions, as long as the chosen functions
are \CUASGen-acceptable.

@@

@@

        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],\scid,\msg) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\cscid_0,\attrs)) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\cscid_1,\attrs)): \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{description}
\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. Requires users to
  prove knowledge of \usk and the related \upk. It also requires that any
  additional credential supporting the request be a valid credential (signed by
  some issuer) and bound to \upk, and enforces the corresponding \fissue policy.
\item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. Ensures that
  signatures ``encode'' the correct signature evaluation and opening values, and
  that any credential used to create the signature is bound to the same \upk.
\item[$\NIZKRel_{\Open}$:] For NIZK proofs at opening time. Ensures that the
  utility information extracted by the \Open algorithm is correct.
\end{description}

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

From them, we build \CUASGen as follows.

\paragraph{$\parm \gets \Setup(\secpar)$.} %
The setup process essentially generates the public parameters for all the
building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
\SBCMSetup(\secpar)$, $\Eparm \gets \ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets
\NIZKSetup^{\NIZKRel_{\Issue}}(\secpar)$, $\NIZKcrs_{\Sign} \gets
\NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and $\NIZKcrs_{\Open} \gets
\NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $(\Cparm,\SBCMparm,\Eparm,
\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open})$.

@@

\paragraph{$(\upk,\usk) \gets \KeyGen(\parm)$.} %
Each user first parses \parm as $(\cdot,\SBCMparm,\cdot,\cdot,\cdot,\cdot)$.
Then, runs $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,
\SBCMvk)$, $\usk \gets \SBCMsk$, and returns $(\upk,\usk)$.

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
Each opener parses \parm as $(\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot)$.
Then, runs $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, and sets, $\opk \gets (\Eek,
\finsp)$, and $\osk \gets \Edk$.

\paragraph{$\ipk \gets \ISet((\upk,\usk),\fissue)$.} %
A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
publishes \ipk.

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\cidu,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
  \attrs),\Issue(\isk,\cidi,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
attests attributes $\cattrs_i$. The user requests a signature on a commitment to
the user key, as well as on $\cid=(\cidi,\cidu)$ and the attributes in \attrs.
In addition, the user proves correct computation of the \fissue function set by
the issuer based on the $\cred_i$ credentials and its user public key.
This is essentially achieved through an execution of an \SBCM interactive
signing protocol with $\NIZKRel_{\Issue}$ as NP relation. Since \fissue is
evaluated by the user, but depends on the \cidi value chosen by the issuer, the
issuer first needs to send \cidi.
Then both interact to produce the \SBCM signature, where the
user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
\cattrs_i,\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the
issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
\rbrace_{i\in[n]})$. The credential \cred produced by the user is the result of
the interactive signing protocol, whereas the issuer produces $(\yissue,
\utrans)$, where \yissue is the output of \fissue, and \utrans is the
communication transcript of the signing protocol.% , which is a $(\Ccom,(\cid,\attrs),\lbrace
% \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple (see \appref{sapp:sbcm} for details).

\paragraph{$\Sig \gets \Sign(\usk,\opk,
  \sCred=(\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)\rbrace_{i\in[n]}),
  \msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
The user first evaluates $\Yeval = (\yeval^0,\yeval^1) \gets \feval (\upk,
\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$. Then, parses \opk as $(\Eek,
\finsp)$, computes $\yinsp \gets \finsp((\yeval^0,\yeval^1),\upk,
\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
\yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r')$ for some fresh
randomness $r'$. Finally, the user
computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
\lbrace(\cid_i,\cattrs_i,\cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r),(\msg,
\feval,\yeval^0,\cinsp,\lbrace \ipk_i\rbrace_{i\in[n]},\Eek))$ and outputs
$(\sig = (\NIZKproof,\cinsp),\yeval^0)$. Note that, depending on the value of
\Yeval and \yinsp, the user may decide to abort
the signing if the resulting values are too privacy-threatening.

@@

\begin{theorem}[Issuance anonymity of \CUASGen]
  \label{thm:issue-anonymity-uas}
  If the \SBCM scheme is blinding, the NIZK system used for $\NIZKRel_{\Issue}$ 
  is zero-knowledge, and \fissue is a \CUASGen-acceptable function, our \CUASGen
  construction satisfies issuance anonymity as defined in
  \defref{def:issue-anonymity-uas}.
\end{theorem}
